SDM\_the\_search\_for\_powers\_of\_2\_everywhere

### 2018-05-03 Chapters/Chapter01.tex
Minor typo

According to \citet{barber2012bitter}, despite the 30-year literature on e-cash, most of the proposed schemes requires a central authority which controls the currency issuance and prevents double spending \citep{chaum1983blind, okamoto1995efficient, camenisch2005compact, canard2007divisible}. Some papers even propose solutions in a similar trajectory to Bitcoin, such as hash chain \citep{zongkai2004new} and preventing double spending using peer-to-peer networks \citet{osipkov2007combating, hoepman2007distributed}. The no central point of trust and predictable money supply together with a clever solution to the double-spending problem is what separates Bitcoin from the previous e-cash philosophies.

>>>>

According to \citet{barber2012bitter}, despite the 30-year literature on e-cash, most of the proposed schemes requires a central authority which controls the currency issuance and prevents double spending \citep{chaum1983blind, okamoto1995efficient, camenisch2005compact, canard2007divisible}. Some papers even propose solutions in a similar trajectory to Bitcoin, such as hash chain \citep{zongkai2004new} and preventing double spending using peer-to-peer networks \citep{osipkov2007combating, hoepman2007distributed}. The no central point of trust and predictable money supply together with a clever solution to the double-spending problem is what separates Bitcoin from the previous e-cash philosophies.
